Peptide retention time prediction

### 2015-01-27 retention.tex
after spell-check

However, despite all these efforts, it should be pointed out that none
of the retention time prediction methods currently available is able
to provide accuracies comparable to the small shifts observed when
running a sample twice through a chromatography column
(Figure \ref{fig:repr}). Recently, the lack of suitable
representations for secondary structure elements was indicated as one
of the main causes of prediction errors \cite{Reimer2012}.  Most
probably additional factors are involved, and further endeavors are
required to reach the desired level of accuracy.

>>>>

However, despite all these efforts, it should be pointed out that none
of the retention time prediction methods currently available is able
to provide a prediction precision comparable to the small shifts
observed when comparing retention time of peptides from two technical
replicates (Figure \ref{fig:repr}). Recently, the lack of suitable
representations for secondary structure elements was indicated as one
of the main causes of prediction errors \cite{Reimer2012}.  Most
probably additional factors are involved, and further endeavors are
required to reach the desired level of accuracy.
